### 2022-11-14 briefcommunicaton/briefcommunication.tex
#37: Introduction (1)

\section{\label{sec:level1}Introduction}

@@

\ref{fig:test}

@@

% BIBLIOGRAPHY ==============================================================================================================

\nocite{*}
\bibliography{references.bib}% Produces the bibliography via BibTeX.

>>>>

%%% INTRODUCTION ===========================================================================================================

It is known that radially sheared zonal flows plays a significant role in nonlinear stabilization in tokamak plasmas. \cite{WACooper1988,doi:10.1063/1.859529,doi:10.1063/1.873896}. 
Through advection on the sheared zonal flows the turbulent structure in plasma gets deformed and tilted that causes an $E \times B$ nonlinearty. \cite{doi:10.1063/1.859529, doi:10.1063/1.871313, doi:10.1063/1.872367}
Zonal flows mediate spectral energy transfer to larger radial wave vectors. \cite{doi:10.1063/1.3033206, doi:10.1063/1.3675855, PhysRevLett.120.175002}
The strength of the shearing process is the $E \times B$ shearing rate $\omega_{\mathrm{E \times B}}$ which is the radial derivative of the advecting zonal flow velocity. \cite{doi:10.1063/1.871313, doi:10.1063/1.872847}
The shearing rate $\omega_{\mathrm{E \times B}}$ is defined as 
\begin{equation}
	\omega_{\mathrm{E \times B}} = \frac{1}{2} \frac{\partial^2 \langle \Phi \rangle}{\partial \psi^2}
	\label{eq:shearingrate}
\end{equation}
where $\langle \Phi \rangle$ is the zonal electrostatic potential and $\psi$ the radial coordinate that labels the flux surfaces. \cite{doi:10.1063/1.4952621, doi:10.1063/1.5035184, doi:10.1063/1.3005380}
It was shown that the nonlinear threshold for turbulence is directly related to shear stabilization. \cite{doi:10.1063/1.873896} 
Often the shear stabilization is expressed in the empirical Waltz rule $\omega_{\mathrm{E \times B}} \sim \gamma$, \cite{doi:10.1063/1.870934, doi:10.1063/1.872847} where $\gamma$ is defined as the maximum linear growth rate in the unstable mode. In the discovered zonal flows, also known as $E \times B$ staircase \cite{PhysRevE.82.025401}, exhibit amplitudes in terms of the $E \times B$ shearing rate satisfying the stabilization criteria. \cite{doi:10.1063/1.4952621, doi:10.1063/1.4961231}

@@

@@

% BIBLIOGRAPHY =============================================================================================================

%\nocite{*}
\bibliography{references.bib}% Produces the bibliography via BibTeX.
